**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-03-07 Manuscripts/Manuscript_AM_v3.Rmd
working on plot for basis functions

```{r,basis-functions}

@@

  dat<-subset(dat,treatment==1)
  dat<-dat[,c('y','time')]
gm<-gam(y~s(time,k=5),data=dat)
model_matrix<-predict(gm,type='lpmatrix')

x_new <- as.data.frame(seq(0, max(dat$time), length.out = 100))
y_pred <- predict(gm, data.frame(x = x_new))

matplot(dat$time, model_matrix[,-1], type = "l", lty = 2, add = T)

>>>>

```{r,basis-functions}
library(mgcv)
library(mvnfast)
  library(nlme)
  library(ggsci)
library(tidyverse)

@@

  dat<-subset(dat,treatment==1)
  dat<-dat[,c('y','time')]
gm<-gam(y~s(time,k=5),data=dat)
model_matrix<-as.data.frame(predict(gm,type='lpmatrix'))

x_new <- (seq(0, max(dat$time), length.out = 100))
y_pred <- predict(gm, newdata=dat)

time<-c(1:6)

basis<-model_matrix[1:6,-1] #extracting basis
basis<-basis %>% #pivoting to long format
  pivot_longer(
    cols=starts_with("s")
  )%>%
  arrange(name) #ordering

#length of dataframe to be created: number of knots by number of timepoints (minus 1 for the intercept that we won't plot)
ln<-length(basis1)*(length(coef(gm))-1)

basis_plot<-data.frame(Basis=integer(ln),
                       value=double(ln),
                       time=integer(ln),
)

basis_plot$time<-rep(time) #pasting timepoints
basis_plot$Basis<-rep(1:4,each=6) #pasting basis number values
basis_plot$value<-basis$value #pasting basis values

ggplot(basis_plot,aes(x=time,y=value))+geom_line()+facet_grid(~Basis) #plotting

#plot(dat$y~dat$time)

#matplot(dat$time, model_matrix[,-1], type = "l", lty = 2, add = T)

#lines(y_pred ~ dat$time, col = "red", lwd = 2)
